Estimation of Manning's Friction Coefficient using DART Buoys Data during \tohoku Tsunami

### 2013-12-23 paper/intro.tex
Minor wording change

\section{Introduction}

Tsunamis in the past decade have been responsible for some of the most deadly and costly natural disasters ever recorded.  Coastal communities have faced this hazard by assessing the risk of these hazards, attempting to make informed decisions about the likelihood that such an event would occur with cost to life and property.  To do this, computational models of tsunami events are often employed to explore multiple different scenarios.  Unfortunately, since tsunami events are relatively rare, there is an abundance of uncertainty in the input data for these computational models ranging from effects of the domain such as bathymetry and friction parameterizations, to the earthquake source.  In this article we present an approach to quantifying the uncertainty in the friction field and a method to find the best parameterized values of the friction field using the \tohoku tsunami as a case study.

>>>>

\section{Introduction}
\alert{We need to unify the name of the input parameters, Manning coefficint or friction or roughness.
what is the best name ??}

Tsunamis in the past decade have been responsible for some of the most deadly and costly natural disasters ever recorded.  Coastal communities have faced this hazard by assessing the risk they pose, attempting to make informed decisions about the likelihood that such an event would occur with cost to life and property.  To do this, computational models of tsunami events are often employed to explore multiple different scenarios.  Unfortunately, since tsunami events are relatively rare, there is an abundance of uncertainty in the input data for these computational models ranging from effects of the domain such as bathymetry and friction parameterizations, to the earthquake source.  In this article we present an approach to quantifying the uncertainty in the friction field and a method to find the best parameterized values of the friction field using the \tohoku tsunami as a case study.
